Dynein project log

### 2016-11-17 thesis_stuff/thesis_stuff.tex
tweak thesis version of estimate for rate (but not code)
add note about time between steps to thesis_stuff

\begin{align*}
  k_{bind} &= Ae^{-\beta(\Delta G_{bind} + \Delta G_{conf})}\\
  k_{bind} &= \left(Ae^{-\beta\Delta G_{bind}}\right)e^{-\beta\Delta G_{conf}}\\
  k_{bind} &= Be^{-\beta\Delta G_{conf})}\hspace{2cm}\mbox{B constant at constant T}\\
  \left<k_{bind}\right> &= \left<Be^{-\beta\Delta G_{conf}}\right>\\
  \left<k_{bind}\right> &= Be^{-\beta\Delta \left<G_{conf}\right>}\\
  \left<\Delta G_{conf}\right> &= \left(4-2\right)\left(\frac{1}{2}k_BT\right) = \beta^{-1}\\
  \left<k_{bind}\right> &= Be^{-1}\\
  \rightarrow B &= \frac{k_{bind}}{e}\\
\end{align*}

@@

>>>>

\begin{align*}
  k_{bind} &= Ae^{-\beta(\Delta G_{bind} + \Delta G_{conf})}\\
  k_{bind} &= \left(Ae^{-\beta\Delta G_{bind}}\right)e^{-\beta\Delta G_{conf}}\\
  k_{bind} &= Be^{-\beta\Delta G_{conf})}\hspace{2cm}\mbox{B constant at constant T}\\
  \left<k_{bind}\right> &= \left<Be^{-\beta\Delta G_{conf}}\right>\\
  \left<k_{bind}\right> &= Be^{-\beta\Delta \left<G_{conf}\right>}\\
  \left<\Delta G_{conf}\right> &= \frac{1}{2}k_BT = \frac12\beta^{-1}\\
  \left<k_{bind}\right> &= Be^{-1/2}\\
  \rightarrow B &= \frac{k_{bind}}{\sqrt{e}}
\end{align*}

@@

\section{Notes by David}
(This stuff can be deleted or edited or moved elsewhere...)

The mean speed of dynein is $134\pm 60$~nm~s$^{-1}$.

Its average step 1D displacement is 8~nm. (See page 194 of Weihong's \emph{Nature} paper.)

Together this means that the mean time between steps is about 60~ms.
Note milliseconds.  Thus we really need to be careful about how small
our $\Delta t$ is.
